---
title: "Base_R_Code"
format: html
editor: visual
---

## Task 1: Basic Vector Practice

1.  Creating the vectors for the pre and post treatment values

```{r}
pre_treat <- c(120, 151, 125, 126, 115, 132, 132, 129, 134, 139, 127, 122, 127, 135, 133, 128, 147, 138, 140, 132)

post_treat <- c(127, 145, 135, 122, 115, 122, 123, 126, 126, 129, 132, 146, 120, 114, 121, 120, 128, 120, 133, 115)
```

2.  Assigning names to the vectror elements

```{r}
pre_subjects <- paste("Subject", 1:20, sep = "_")
names(pre_treat) <- pre_subjects
pre_treat

post_subjects <- paste("Subject", 1:20, sep = "_")
names(post_treat) <- post_subjects
post_treat

```

3.  Calculating the change in blood pressure

```{r}
bp_change <- pre_treat - post_treat
bp_change
```

4.  Finding the average blood pressure change

```{r}
mean(bp_change)
```

5.  Finding patients that experienced a decrease in blood pressure

```{r}
dec_bp <- which(bp_change > 0)
dec_bp_sub <- names(bp_change)[dec_bp]
dec_bp_sub
```

6.  Subset returning subjects with a positive change

```{r}
bool_dec_bp <- bp_change > 0 
bool_dec_bp
```

7.  Calculating average decrease in blood pressure

```{r}
avg_dec_bp <- mean(dec_bp)
avg_dec_bp
```

## Task 2: Basic Data Frame Practice

1. Creating a data frame
```{r}
patients <- paste("subject", 1:20, sep = "_")
bp_df <- data.frame(patients, pre_treat, post_treat, bp_change)
bp_df
dim(bp_df)
```

2. Rows where difference is negative
```{r}
subset <- bp_df[bp_df$bp_change < 0, ]
subset
```

3. Adding a new column
```{r}
bp_df$bp120 <- c(post_treat < "120")
```

4. Printing out data frame
```{r}
knitr::kable(bp_df)
```

## Task 3: List Practice

Entering the placebo treatment numbers
```{r}
plac_pre_treat <- c(138, 135, 147, 117, 152, 134, 114, 121, 131, 130)
plac_post_treat <-c(105, 136, 123, 130, 134, 143, 135, 139, 120, 124)
```

1. Creating new placebo patient data frame
```{r}
plac_patients <- paste("subject", 1:10, sep = "_")
plac_bp_change <- plac_pre_treat - plac_post_treat
plac_bp120 <- plac_post_treat < "120"
plac_bp_df <- data.frame(plac_patients, plac_pre_treat, plac_post_treat, plac_bp_change, plac_bp120)
plac_bp_df
```

2. Creating the list with two elements
```{r}
bp_list <- list(treatment = bp_df, placebo = plac_bp_df)
bp_list
```

3. Accessing the first list element
```{r}
bp_list[1]
str(bp_list[1])
bp_list$treatment

```

4. Accessing the pre_treat column of placebo data
```{r}
bp_list$placebo$plac_pre_treat
```